---

title: "Peer Assessment 1"
output: html_document
---

This is a submission for Reproduceable Reasearch, peer assessment 1.

First load the data into a data frame named "activity" and load lattice and plyr.

```{r}
setwd("~/Documents/CourseraDS")
activity = read.csv("activity.csv")
library(package = "lattice")
library(plyr)
```

#Transform the data

Change date column to be in date format

```{r}
activity$date <- as.Date(activity$date)
```

Ignore missing values

```{r}
activity_c <- activity[complete.cases(activity),]
```




#What is mean total number of steps taken per day?

Create a data set grouped by day:
```{r}
activity_byDay <- aggregate(activity_c$steps, by=list(date = activity_c$date), FUN = sum)
```

Histogram of steps by day: 

```{r}
hist(activity_byDay$x)
```


Mean:
```{r}
mean(activity_byDay$x)
```

Median
```{r}
median(activity_byDay$x)
```


#What is the average daily activity pattern?

Create dataframe grouped by interval

```{r}
activity_byInt <- aggregate(activity_c$steps, by=list(Int = activity_c$interval), FUN = mean)
```

Plot average activity by interval

```{r}
plot(activity_byInt$Int,activity_byInt$x, type = "l")
```

The interval with the max average step count

```{r}
max_step <- max(activity_byInt$x)
activity_byInt[activity_byInt$x == max_step,]
```

#Imputing missing values


Number of missing values.

```{r}
sum(is.na(activity))
```

I will replace missing values with the mean of steps in the cleaned dataframe.

```{r}
meanStep <- mean(activity_c$steps)
activity_impute <- activity
activity_impute[is.na(activity_impute)] <- meanStep
```

Group the cleaned data by day.
```{r}
activity_imp_byDay <- aggregate(activity_impute$steps, by=list(date = activity_impute$date), FUN = sum)
```

Make a histogram. Multiply by 1 to force coercian from factor.
```{r}
hist(activity_imp_byDay$x * 1)
```

Mean:
```{r}
mean(activity_imp_byDay$x)
```

Median
```{r}
median(activity_imp_byDay$x)
```

The imputation of missing values has the effect of making the median very close to the mean. The histogram also has a higher frequency in the center bucket.

#Differences between weekdays and weekends

Modify data set to contain weekday data
```{r}
activity_impute[,'Weekday'] = weekdays(activity_impute$date)
activity_impute[,'IsWeekend'] <- ifelse((activity_impute$Weekday == "Saturday" | activity_impute$Weekday == "Sunday"), "Weekend","Weekday" )
```

Create dataframe grouped by interval

```{r}
activity_imp_byInt <- aggregate(activity_impute$steps, by=list(Int = activity_impute$interval,IsWeekend = activity_impute$IsWeekend), FUN = mean)
```

Graph the results.
```{r}
xyplot(x ~ Int | IsWeekend, data = activity_imp_byInt, type = "l",layout = (c(1,2)))
```

```{r}

```

```{r}

```

```{r}

```

```{r}

```


```{r}

```

```{r}

```

```{r}

```
=======
title: "Reproducible Research: Peer Assessment 1"
output: 
  html_document:
    keep_md: true
---


## Loading and preprocessing the data



## What is mean total number of steps taken per day?



## What is the average daily activity pattern?



## Imputing missing values



## Are there differences in activity patterns between weekdays and weekends?
>>>>>>> 80edf39c3bb508fee88e3394542f967dd3fd3270
